---
  title: "Pker texas hold'em"
output: html_document
date: "2023-11-15"
---
  
  Creación del mazo de cartas, se crea como un data frame

```{r deck}
deck <- data.frame(
  face = c("king", "queen", "jack", "ten", "nine", "eight", "seven", "six",
           "five", "four", "three", "two", "ace", "king", "queen", "jack", "ten", 
           "nine", "eight", "seven", "six", "five", "four", "three", "two", "ace", 
           "king", "queen", "jack", "ten", "nine", "eight", "seven", "six", "five", 
           "four", "three", "two", "ace", "king", "queen", "jack", "ten", "nine", 
           "eight", "seven", "six", "five", "four", "three", "two", "ace"),  
  suit = c("spades", "spades", "spades", "spades", "spades", "spades", 
           "spades", "spades", "spades", "spades", "spades", "spades", "spades", 
           "clubs", "clubs", "clubs", "clubs", "clubs", "clubs", "clubs", "clubs", 
           "clubs", "clubs", "clubs", "clubs", "clubs", "diamonds", "diamonds", 
           "diamonds", "diamonds", "diamonds", "diamonds", "diamonds", "diamonds", 
           "diamonds", "diamonds", "diamonds", "diamonds", "diamonds", "hearts", 
           "hearts", "hearts", "hearts", "hearts", "hearts", "hearts", "hearts", 
           "hearts", "hearts", "hearts", "hearts", "hearts"), 
  value = c(13, 12, 11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 13, 12, 11, 10, 9, 8, 
            7, 6, 5, 4, 3, 2, 1, 13, 12, 11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 13, 12, 11, 
            10, 9, 8, 7, 6, 5, 4, 3, 2, 1)
)
```



```{r}



shuffle <- function(deck) { 
  random <- sample(1:52, size = 52)
  deck[random, ]
}

shuffle_deck <- shuffle(deck)

dealer <- function(shuffle_deck, n){
  
  cards_per_player <- 2
  players <- vector("list", length = n)
  
  for(i in 1:n){
    firts <- (i - 1) * cards_per_player + 1
    last <- 2*i
    players[[i]] <- shuffle_deck[firts:last, ]
    
  }
  
  remaining_cards <- shuffle_deck[(n * cards_per_player + 1):(n * cards_per_player + 5), ]
  
  list(players = players, table = remaining_cards)
}

numPlayers <- 2

players <- dealer(shuffle_deck, numPlayers)

for (i in 1:numPlayers) {
  print(players$players[[i]])
}
cat("table cards: ")
print(players$table)


```
#function to extract and sort the cards 
sort_cards <- function(hand_Table,hand_Player){
  cards <- merge(hand_Table,hand_Player, all = TRUE)
  sort_c <- ordenado <- cards[order(cards$value),]
  return(sort_c) 
}

prueba <- sort_cards(players$table,players$players[[2]])
head(prueba)

prueba[1,3]

#function for royal flush 
royal_flush <- function(cards){
  n=6
  counter = 0
  straigh = TRUE
  Flush = FALSE
  if(cards[1,3] == 1 & cards[7,3] == 13){
    while (straigh & n>1) {
      if((cards[n,3] == (cards[n+1,3]-1)) & counter<3){
        counter = counter +1
      }
      if((cards[n+1,3]-cards[n,3]) > 1 & counter<3){
        straigh = FALSE
      }
      n = n-1
    }
    
    s = 0
    c = 0
    h = 0
    d = 0
    
    cards[1,3] = 14
    
    for (i in 1:7) {
      if(cards[i,2] == "spades"){
        s = s + cards[i,3]
      }
      if(cards[i,2] == "clubs"){
        c = c + cards[i,3]
      }
      if(cards[i,2] == "hearts"){
        h = h + cards[i,3]
      }
      if(cards[i,2] == "diamonds"){
        d = d + cards[i,3]
      }
    }
    
    if(d >= 60 | c >= 60 | s >= 60 | h >= 60){
      Flush = TRUE
    }
    
    if(straigh & Flush){
      return(c(10,14))
    }
    if(straigh & !Flush){
      return(c(5,14))
    }
    if(!straigh & !Flush){
      return(c(0,0))
    }
  }
  return(c(0,0))
}

prueba_royal_flush <- data.frame(
  face = c("king", "queen", "jack", "ten", "ace"),  
  suit = c("spades", "spades", "spades", "spades", "spades"), 
  value = c(13, 12, 11, 10, 1)
)

prueba_mano <- data.frame(
  face = c("king", "queen"),  
  suit = c("hearts", "hearts"), 
  value = c(13,12)
)

prueba_royal_flush <- sort_cards(prueba_royal_flush,prueba_mano)
head(prueba_royal_flush)

resultado <- royal_flush(prueba_royal_flush)
resultado






